\documentclass{article}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{indentfirst}   % Indents first paragraph. change if u want ig
\usepackage{setspace} 
\doublespacing

\begin{document}
\title{\textbf{Milestone 3}}
\author{Spencer Hirsch}
\date{\today}

\maketitle

\section*{Assignment Goal}
The goal of this assignment is to help you understand and analyze the main
components of a senior project. This can help you later to understand, analyze,
develop, and improve your own senior design project.

\section*{Tasks for this assignment}
When you enroll in senior projects you will be required to complete various tasks.
Tasks for this assignment are: \\
\begin{itemize}
    \item Approach a \textit{faculty} member who could help guide you through the
          successful completion of a senior project.
          \begin{itemize}
            \item Ask if they have a project you could work on.
            \item If you have a project in mind, explain it to them and ask for their
                  feedback.
          \end{itemize}
          If you don't get the help you need, approach another member of the faculty.
          Repeat as needed.
    \item In senior projects you will be required to write several software engineering
           documents that describe what is to be done for your project and how you plan to do it.
           Dr. Chan has an excellent collection of guideliners and other resources to help students
           successfully complete a senior project: \href{https://cs.fit.edu/~pkc/classes/seniorProjects/}{See his projects page}
           and read these documents:
    \item Guidelines for Role of Faculty Sponsors
    \item Guidelines for a Project plan
    \item Guidelines for your Project Web Sites
    \item Guidelines for Milestone Progress Evaluations
    \item Guidelines for Requirements, Design, Test documents
    \item Guidelines for Scopres for teammates
    \item Guidlines for Demo Video and User/Developer Manual
    \item \href{https://www.fit.edu/policies/student-handbook/}{the intellectual propery policies in the student handbook}
    \item \href{https://www.fit.edu/policies/faculty/}{the intellectual propery policies in the faculty handbook}
    \item \href{https://www.fit.edu/engineering-and-science/academics-and-learning/student-design-and-research}{the COES Student Design and Research website}
    \item Write a report based on your interviews and readings following this outline:
          \begin{enumerate}
            \item Your name: \textbf{Spencer Hirsch}
            \item The names of faculty member(s) you approached: \textbf{Dr. Hohlmann}
            \item Did they have projects they were interested in having you help? 
            If so, summarize their project(s). \\

                  I am currently doing research with Dr. Hohlmann's CMS group. I am working closely with a graduate student on the analysis of
                  proton-proton collisions. We just completed hyper-parameter tuning a machine learning model to accurately predict dimuon pairs
                  from off-shell parent particles. There are many different groups within Dr. Hohlmann's HEP research group and it is always interesting
                  to hear about what everyone is working on. Other pairs are working on hardware, while others like myself are working on analysis. \\


            \item Did you tell them about a project you would like to do? If so, what was their reaction? \\

                  I don't have any ideas as of right now, I've begun putting greater thought into what I want to do. \\

            \item Based on your reading of the Guidelines the intellectual policies in the student and Faculty
                  handbooks, and exploring the college website for design and research write a paper that describes
                  what you have leared and will be useful to you in creating your own Senior Project. \\

                  Student Design and Research \\

                  The purpose of student design and research is so that students are able to get hands on experience in their field of 
                  study. All of the senior design and showcase porjects are shown at the Design Showcase where they present their work. 
                  There is judging crieteria for the event as well, both for the engineering fields as well as the science fields, both 
                  80 and 60 points, respectively. For the engineering criteria, the categories are based on, Project Definition, Requirements, 
                  Overall Presentation, Classroom knowledge, Engineering and Scientific Design Principle, Team/Project Management, and Project 
                  Impact. \\

                  Student Handbook \\

                  Under the Intellectual Property Policy for Students, states that any intellectual propery developed by the students is owned by
                  the university if the students were employed by the university or received external funds at the point of the discovery. This 
                  also only applies if the discovery happened during the scope of their employment. It also states that the intellectual rights
                  is owned by the university if the student made substantial use of the university facilities in order to make the discovery. The
                  use of facilities is only an important part of the contribution if the facilites used are not available for the majority of the
                  student population at Florida Tech. \\
                  
                  Faculty Handbook \\

                  Under the Policy on Patents and Copyrights, Ownership and Discoveries and Inventions section it states, the ownership of a discovery
                  as a result of regular duties or research done in connection with theses or dissertations, the ownership will be given to either the
                  university or a determined person. The discovery or invention developed by faculty without the university contributing anything substantial
                  or essential, the ownership will be given the faculty member. The discovery will also be awared to the faculty member if the development was
                  done on their own time. After reading throught this section under the faculty handbook it seems as though the university is committed to
                  giving credit where credit is due with respect to the devleopment of an invention or other intellectual property. It is reasonable to see that
                  if the university facilities are extensively used or any resources are extinguised during the development of the discovery the credit will be given
                  the university. The univeristy also holds a board that can determine whether or not the property is owned by the university or the individuals
                  that worked towards the discovery of the propterty. \\

                  

            \item Describe one or more projects you would like to pursue as a senior. Do you have teammates? \\
            
                  As of right now, I don't have any of my own ideas, however, I do like the idea of continuing to work with Dr. Hohlmann's HEP
                  group to contribute more of my knowledge of computer science to the physics-oriented group. Yes, I do have potential teammates
                  for a Senior Desing project.
            
                  
          \end{enumerate}
\end{itemize}

\section*{Submitting your report}

Your report must be double-spaced, written using 12-point font, with 1-inch top, bottom, left \& right margins,
store in PDF format, and submitted on Canvas.

\end{document}