\documentclass{article}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{indentfirst}   % Indents first paragraph. change if u want ig
\usepackage{setspace} 
\doublespacing

\begin{document}
\title{\textbf{Milestone 2}}
\author{Remington Greok, Tyler Gutowski, Spencer Hirsch, Thomas Johnson}
\date{\today}

\maketitle

\section{\textbf{Assignment Goal}}
\noindent This assignment is to help you belong to a team either as a leader or a
member. Search the terms "team leader" and "team member" to learn about these 
toles to get advice on \textit{teamwork}.

In particular, for this course, you will learn about tools that support software
development and collaboration. Here is a partial list of tools you may want to use.

\begin{itemize}
    \item Microsoft Teams Find resources to learn about \textit{Microsoft Teams}.
    You can access Teams software through the Florida Tech website.
    \item GitHub is perhaps the default site for collaborative software development.
    You should be able to find resources to learn about and use GitHub.
    \item Trello is another site you may find useful.
    \item There are many other tools to help collaboration in the development of 
    computer science/software engineering solutions to problems. If there is some
    you like, let me know.
\end{itemize}

\section{\textbf{Tasks for this Assignment}}

\begin{itemize}
    \item For a team of 2 or 3 students enrolled in this course. (A team of 4 may be
    allowed but must be justified and approved by the instructor.) I believe I've
    had Canvas set up teams.
    \item A a team, write a report following this outline:
    \begin{enumerate}
        \item \textit{Your name?} \\ Spencer Hirsch
        
        \item \textit{Your teammates' names?} \\ Remington Greko, Tyler Gutowski, and Thoams Johnson.
        
        \item \textit{Did you consider using development tools other than ones mentioned above?
        If so, what were they?} \\ No, for the devlopment tool, we will be using GitHub, it
        is a tool that we are all very familiar with and we will continue using it.
        
        \item \textit{Desribe the team work tool you and your teammates have decided to use. If
        there are multiple options, outline them.} \\ We are all very familiar with Discord,
        for this reason we have set up a group to communicate in with respect to the
        assignments for this class. Discord is a very useful tool for communicating as
        it allows for multiple platforms and we are all very responsive on it.
        
        \item \textit{Why did you choose the software devlopment tool you plan to use in senior
        projects?} \\ As mentioned above, we have decided that we will use GitHub while working
        on out project. We have all been using GitHub for a while now and are very familiar with
        Git and how it works. We believe that this will be the best course of action for the
        group.
    \end{enumerate}
\end{itemize}

\section{\textbf{Submitting your report}}

Submit your report on Canvas. I expect erach team member to submit the same report.


\end{document}
